Whittaker Models for Real Groups

### 2024-06-12 whittaker.tex
Small update merging our recent changes

We need to pass to the dual Lie algebra $\g^*$. We follow  \cite[Section 2]{AVAV}.
Define $\N^*\subset \g^*$ to be the set of elements whose orbit is a cone.
We identify $\g$ and $\g^*$ using  a non-degenerate invariant form on $\g$.
This restricts to an isomorphism $\N\simeq \N^*$. Although this isomorphism depends on the choice of form,
the bijection on the level of $G$-orbits is canonical.

We define $\O_p$ to be the principal nilpotent orbit in $\N^*$: this is the unique orbit such that $\overline{\O_p}=\N^*$.

@@

\subsubsection*{Representations}

We need to pass back and forth between representations of $G(\R)$ and $(\g,K)$-modules.
See \cite{greenbook} for details.

Suppose $\pi$ is an irreducible admissible representation of $G(\R)$  on a Hilbert space. 
The underlying
$(\g,K)$-module is on the space of $K$-finite vectors in
$V$. Conversely if $\pi$ is an irreducible $(\g,K)$-module it can be
realized as the $K$-finite vectors of a Hilbert space representation, which we
refer to as the Hilbert space globalization of $\pi$.

\footnote{(AA 2024-V-1) Todo: add notation $\pi_K$ and quickly discuss notions of equivalence?}

@@

The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in $\s^*$, so it is a finite union of
nilpotent $K$-orbits on $\s^*$. See \cite[Section 5]{vogan_bowdoin}.

@@

@@

Part~(c) follows from~\cite[Lemma B]{rossmann_limit_orbits}. Let us briefly explain how to go from there to  assertion~(c), using standard facts on the asymptotic cone recalled below in Section~\ref{sec:asymp_cone} below.

@@

\begin{theorem} \label{th:main} Suppose~$\Pi$ is an $L$-packet of discrete series for~$G(\R)$. 
The maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$ induce bijections between:
\begin{enumerate}
\item[(1)] The set~$\Pi_{\mathrm{gen}}$ of generic discrete series representations in~$\Pi$ ;
\item[(2)] The set of Whittaker data for $G(\R)$ ;
\item[(3)] The set of~$K$-orbits on $\mathcal{O}_p \cap \s^*$.
\item[(4)] The set of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)^*$.
\end{enumerate}
In particular if $\pi$ is a large discrete series represenation then each of these three invariants of $\pi$ determines the other $2$. 
\end{theorem}

@@

Then $F_\pi\in\s$ is a regular nilpotent element. Let $\xi_\pi\in \N^*$ be the corresponding element (cf. Section \ref{s:nilpotentorbits}).
Then 
$$
\AV(\pi)=\overline{K\cdot \xi_\pi}.
$$
\end{lemma}

>>>>

We need to pass to the dual Lie algebra $\g^*$. We follow  \cite[Section 2]{AVAV}.
Define $\N^*\subset \g^*$ to be the set of elements whose orbit is a cone.
We identify $\g$ and $\g^*$ using  a non-degenerate invariant bilinear form on $\g$. Given an element~$X$ in $\g$ we sometimes write $X^\ast$ for the corresponding element of~$\g^\ast$.

This restricts to an isomorphism $\N\simeq \N^*$. Although this isomorphism depends on the choice of form,
the bijection on the level of $G$-orbits is canonical.

We define $\O_p$ to be the \emph{principal nilpotent orbit} in $\N^*$: this is the unique orbit whose closure is  $\N^*$.

@@

\subsubsection*{Representations} 
We need to pass back and forth between representations of $G(\R)$ and $(\g,K)$-modules.
See \cite{greenbook} for details.

Suppose $\pi$ is an irreducible admissible representation of $G(\R)$  on a Hilbert space. 
The underlying
$(\g,K)$-module is on the space of $K$-finite vectors in
$V$; we will denote it by~$\pi_K$ in this paper.

Conversely if $\pi$ is an irreducible $(\g,K)$-module it can be
realized as the $K$-finite vectors of a Hilbert space representation, which we
refer to as the Hilbert space globalization of $\pi$.

The notion of equivalence of $(\g, K)$-modules is defined in such a way that two equivalent $(\g, K)$-modules have equivalent Hilbert space globalizations, and that any two equivalent admissible representations of~$G$ have equivalent underlying $(\g, K)$-modules.

@@

The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in~$\s^*$; so it is a finite union of
nilpotent $K$-orbits on $\s^*$. See \cite[Section 5]{vogan_bowdoin}.

@@

\subsection{Discrete series and Harish-Chandra parameters}

Recall $G(\R)$ has relative discrete series representations if and only if it has a relatively compact Cartan subgroup. From now on, we assume $G(\R)$ does have discrete series representation, and fix a compact Cartan subgroup $H(\R)$ of~$G(\R)$, with complexified Lie algebra~$\mathfrak{h} \subset \g$.

With this choice, any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}. Etc etc.
\begin{itemize}
\item Harish-Chandra parameter, $W$ and $W_K$
\item Notion of large Weyl chamber 
\end{itemize}

@@

Part~(c) follows from~\cite[Lemma B]{rossmann_limit_orbits}. Let us explain how to go from there to  assertion~(c), using standard facts on the asymptotic cone recalled below (\S\,{}\ref{sec:asymp_cone}).

@@

\begin{theorem} \label{th:main} Suppose~$\Pi$ is an $L$-packet of discrete series for~$G(\R)$. 
The maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$ induce bijections between:
\begin{enumerate}
\item[(1)] The set~$\Pi_{\mathrm{gen}}$ of generic discrete series representations in~$\Pi$ ;
\item[(2)] The set of Whittaker data for $G(\R)$ ;
\item[(3)] The set of~$K$-orbits on $\mathcal{O}_p \cap \s^*$.
\item[(4)] The set of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)^*$.
\end{enumerate}
In particular if $\pi$ is a large discrete series representation then each of these three invariants of $\pi$ determines the other two. 
\end{theorem}

@@

Then $F_\pi\in\s$ is a regular nilpotent element. Let $F_\pi^\ast\in \N^*$ be the corresponding element (cf. Section \ref{s:nilpotentorbits}).
Then 
$$
\AV(\pi)=\overline{K\cdot F_\pi^\ast}.
$$
\end{lemma}
